Analysis of Bauer et al. (unpublished) Field experiment: <br> Persistence

### 2022-12-05 R/model_persistence_check.Rmd
Update all persistence models

---
title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Persistence"
author: "<b>Markus Bauer*</b> <br>"
date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
output:
  github_document:
    toc: true
    toc_depth: 3
    dev: png
    fig_width: 7
    fig_height: 5
    df_print: tibble
---

@@

```{r collapse = TRUE}
load(file = here("outputs", "models", "model_persistence_1.Rdata"))
load(file = here("outputs", "models", "model_persistence_full.Rdata"))
m_1 <- m1
m_2 <- m_full
```

>>>>

---
title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Persistence"
author: "<b>Markus Bauer*</b> <br>"
date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
output:
  github_document:
    toc: true
    toc_depth: 3
    dev: png
    fig_width: 7
    fig_height: 5
---

@@

```{r collapse = TRUE, message = FALSE}
load(file = here("outputs", "models", "model_persistence_2.Rdata"))
load(file = here("outputs", "models", "model_persistence_full.Rdata"))
m_1 <- m2
m_2 <- m_full
```
